\documentclass[12pt,a4paper]{report}
\usepackage{graphicx}
\usepackage[margin = 2cm]{geometry}
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\renewcommand{\chaptername}{}
\renewcommand*{\arraystretch}{2}

\begin{document}
\thispagestyle{empty}
\begin{center}
\vspace*{0.25cm}
\textbf{\huge{Yogeesh Rajendra}}\\
\vspace*{0.25cm}
\small{\textbf{e-mail : yogeesh.srkvs@gmail.com , Ph No : +91-9480560233}}
\vspace*{0.25cm}
\hline
\vspace*{0.25cm}
\small{Passionate about technologies, face challenges and to contribute to the growth of the organisation}
\end{center}
\hline
\vspace*{0.25cm}
\textbf{\large{Work Experience}}
\begin{itemize}
\setlength{\itemsep}{2pt}
\item College Intern, \textbf{Cisco Systems} [ R\&D, SRTG Unit ] \quad \quad \quad {\hfill Jun 2012 - Aug 2012}
\item Software Developer, \textbf{SuccessFactors} \quad \quad \quad \quad \quad \quad {\hfill Jul 2013 - Nov 2015}
\item Sr. Software Engineer, \textbf{InMobi} \quad \quad \quad \quad \quad \quad {\hfill Nov 2015 - Oct 2017}
\item Software Development Engineer - 2, \textbf{Amazon} \quad \quad \quad \quad \quad \quad {\hfill Oct 2017 - Present}
\end{itemize}
\\
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
\vspace*{0.25cm}
\\
\textbf{\large{Educational Qualification}}\\
\\
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|c|c|c|}
\hline
 \textbf{College} & \textbf{Year Of Completion} & \textbf{Grade}\\
\hline
 {SJCE, Mysuru - B.E ( CS and Engg ) } & June 2013 & CGPA : 9.21 of 10\\
\hline
 {SRKVS, Mysuru - PUC } & Mar 2009 & PCM : 96.67 \% Overall : 93.67 \%\\
 \hline
 {SJCE, Mysuru - B.E ( CS and Engg ) } & Mar 2007 & 91.36 \%\\
\hline
\end{tabular}
\end{center}
\vspace*{0.5cm}
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
\vspace*{0.25cm}
\\
\textbf{\large{Technical Skills}}\\
\\
\hspace*{1.5cm}Languages\hspace*{1.65cm}		:  Java, Shell Scripting, Python, SQL\\
\hspace*{1.5cm}Technologies\hspace*{1.3cm}		:  Linux, Hive, Big Data\\
\end{itemize}
\vspace*{0.25cm}
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
\vspace*{0.25cm}
\\
\textbf{\large{Projects}} 
%\linespread{0.5}

\begin{itemize}
\setlength{\itemsep}{2pt}
{\setlength\itemindent{25pt} \item { \textbf{SIPP XML generator – Using PERL Scripting}\\
\hspace*{1.5cm}Project undertaken in \textbf{Cisco Systems during internship}. Basically a tool to take input of VoIP calls and generate XML files which helps in re generating scenario.}}
{\setlength\itemindent{25pt} \item { \textbf{[ Final Year Project ] Apple Fruit Surface Defect Detection}\\
\hspace*{1.5cm} An image processing project done in MATLAB. This project helps in identifying surface defects on apple fruit. This is applicable only for apple fruits of Golden Delicious kind. Helps in import and export of apple fruit. }}
{\setlength\itemindent{25pt} \item { \textbf{Travel Bureau} \\
\hspace*{1.5cm}Stand alone project done using core java and UI with swings facilitating booking of vehicles of different types for different purposes.}}
{\setlength\itemindent{25pt} \item { \textbf{Paperless Hospital}\\
\hspace*{1.5cm} Design to decrease usage of papers in hospitals. This project submitted for contest named \textbf{IBM-TGMC}. (Used IBM tools for all purposes-\textbf{reached final round})}}
{\setlength\itemindent{25pt} \item { \textbf{Chat App}\\
\hspace*{1.5cm} Stand alone project did for fun using swings facilitating simple chat among systems connected through same access point. (\textbf{Server Socket and Sockets used in J2EE})}}
{\setlength\itemindent{25pt} \item { \textbf{LZW Codec}\\
\hspace*{1.5cm} A technique to losslessly compress text files using LZW algorithm. Implemented using java. [ Data Compression ]}}
\end{itemize}
\end{itemize}
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
\vspace*{0.25cm}
\\
\textbf{\large{Achievements}}
\begin{itemize}
\setlength{\itemsep}{2pt}
{\setlength\itemindent{25pt} \item {Won a HackDay prize for presenting new idea in \textbf{SuccessFactors}.}}
{\setlength\itemindent{25pt} \item { \textbf{Student Coordinator} of organization named Linux Campus Club (LCC-SJCE).}}
{\setlength\itemindent{25pt} \item { Conducting seminars and sessions in various events and tech fests.}}
{\setlength\itemindent{25pt} \item { Runner up in giving punch line for CISCO jabber logo.}}
{\setlength\itemindent{25pt} \item { Stood first in \textbf{Mathematics seminar} competition - District level in 2 PUC.}}
\end{itemize}

\vspace*{0.5cm}
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
\textbf{Links} : {LinkedIn:// \textbf{yogeeshr} | Github:// \textbf{yogeeshr}}

\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}

\flushright
\hfill {Document Powered By {\large{\textbf{\LaTeX}}}}
\flushleft

\end{document}
\documentclass[12pt,a4paper]{report}
\usepackage{graphicx}
\usepackage[margin = 2cm]{geometry}
\renewcommand{\chaptername}{}
\renewcommand*{\arraystretch}{2}
